Model for categorical choice scenarios (experiments 4 to 6)

### 2024-01-18 Experiment_4/model.Rmd
version before more detailed text changes

```{r}
# Tryout beta functions
# ggplot() +
#   geom_function(fun = ~dbeta(.x, shape1 = 0.9, shape2 = 0.9))
```

@@

>>>>

```{r}
# Tryout beta functions
# ggplot() +
#   geom_function(fun = ~dbeta(.x, shape1 = 0.1, shape2 = 10))
```

@@

### Explanation Hugo

We take a very incompetent population

```{r}
# Tryout beta functions
ggplot() +
  geom_function(fun = ~dbeta(.x, shape1 = 0.1, shape2 = 5))
```

We assume many many choice options (approximating a numeric scenario). We look at a very large sample to (hopefully), sample a couple of really competent individuals.

```{r}
# test output (set return to data above)
# test <- simulate_single_population(population = 10000, sample = 10000, options = 10000,
#                                    return = "by degree of majority", distribution = "beta",
#                                    alpha = 0.1, beta = 3) %>% arrange(sample_id) %>%
#   arrange(sample_id)
# 
# test %>% group_by(relative_majority) %>% summarise(across(c(average_relative_competence,
#                                                         average_accuracy),
#                                                       mean)
#                                                )
```

## next

```{r}
# read data for various sample sizes and 3 choice options
test <- read_csv("data/sim_rel_majority_vary_competence_sample_3_options.csv")
```

```{r}
z <- test %>% 
  # filter to scenario with samples of 3
  filter(sample == 3) %>% 
  group_by(competence, relative_majority) %>% 
  summarize(
    mean_competence = mean(average_relative_competence),
    mean_accuracy = mean(average_accuracy),
    absolute_count = n()
    ) %>% 
  group_by(competence) %>% 
  mutate(relative_share = absolute_count / sum(absolute_count),
         bla = sum(absolute_count), 
         relative_majority = round(relative_majority, digits = 2)
         )

ggplot(z, aes(x = as.factor(relative_majority), y = relative_share, fill = competence)) + 
  geom_col(position = "dodge", width = 0.7, color = "white") +
  labs(title = "Grouped Bar Graph",
       x = "Relative Majority",
       y = "Relative Share") +
  scale_fill_viridis_d(option = "rocket") +
  theme_minimal()

z_step2 <- z %>% 
  filter(relative_majority == 0.67)

ggplot(z_step2, aes(x = as.factor(relative_majority), y = relative_share, fill = competence)) + 
  geom_col(position = "dodge", width = 0.7, color = "white") +
  labs(title = "Grouped Bar Graph",
       x = "Relative Majority",
       y = "Relative Share") +
  scale_fill_viridis_d(option = "rocket") +
  theme_minimal()

z_step3 <- z_step2 %>% 
         filter(competence == "very incompetent\n(alpha = 0.1, beta = 1)")

ggplot(z_step3, 
       aes(x = as.factor(relative_majority), y = mean_competence, fill = competence)) + 
  geom_col(position = "dodge", width = 0.7, color = "white") +
  geom_text(aes(label = round(mean_competence, 3)),
            position = position_dodge(width = 0.7),
            vjust = -0.5,    # Adjust vertical position of labels
            size = 3.5,      # Adjust text size
            color = "black") +
  labs(title = "Competence for most likely distribution",
       x = "Relative Majority",
       y = "Average competence") +
  scale_fill_viridis_d(option = "rocket") +
  theme_minimal()

View(z)
```
